Deploying and Sharing QSAR Models using Predictive Modeling Markup Language

### 2014-11-24 paper.tex
Capturing the states of a model training process

>>>>

The initial state is about the dataset. The first instructions of the
algorithm will typically split it into training and validation subsets.
A dataset can be represented using text-based database data formats such
as Comma-Separated Values (CSV), Attribute-Relation File Format (ARFF)
and others. Often becomes necessary to incorporate domain-specific
information. For QSAR, the main need is to provide the description of
the dependent field (a physicochemical property or biological activity)
and independent fields (theoretical molecular descriptors). The goal is
that if the dataset file should be "self-sustainable" if circulated
between parties. An XML-based dataset markup language called QSAR-ML [ref?].

The QsarDB approach [ref?] attempts to capture the initial state, the 
final ending state and all states inbetween using a collection of files
in open and standard data formats. For example, datasets are represented
in TSV, parameter units in UCUM [ref?], bibliography in BibTeX [ref?], 
mathematical relationships in PMML etc. QsarDB leaves the door open
for extension information is user-defined data formats. For example, a
QsarDB archive may capture the primary model object that corresponds to 
the "main" run, as well as all secondary model objects that correspond to 
validation runs.
